DynaProg for Scala

### 2012-11-30 docs/roadmap/design.tex
Nits but not backtrack working (empty), find out why !

Additionally, we need to keep track of the multiplicities of the solutions, that is if we want to obtain the $k$ best solutions, we need to make sure that we return $k$ different backtracks. To do that, we maintain a multiplicity counter at every step: \ul
\item While there is a single solution for all possible incoming paths, we continue in this direction with the same multiplicity (we have no choice).
\item When there is $r$ different solutions available, and the path multiplicity at this point is $k$ we have the following cases: \ol
	\item If $k\ge r$: we explore all paths with multiplicity $k-r+1$. This is because each branch may produce only one solution and we don't know ahead of time which path will provide multiple solutions. Finally, we retain only the $k$ best solutions.
	\item If $k<r$ (there is more paths than needed): we can only explore the $k$ first paths with multiplicity 1 and safely ignore the other (as we only need $k$ results).
	\ole
\ule

@@

Hence for single backtrack we would have at most $O(2n) \cdot O({\rm parser})$ complexity. For the $k$-elements backtrack since we regenerate all possible solutions, that is $O(k^c)$ candidates (with $c$ the maximal number of concatenation in the parser), the overall complexity is $O(2n \cdot k^c) \cdot O({\rm parser})$. Hence there is a $k^c$ factor to pay if we want to backtrack the $k$ best solutions\footnote{Note that the same factor lies in the matrix computation complexity.}.

%Algo: Read matrix, reapply the parser but by maintaining list of origins. Filter results to match multiplicities
% à priori ça a une complexité en k^3*2n pour les k meilleurs backtracks

>>>>

Additionally, we need to keep track of the multiplicities of the solutions, that is if we want to obtain the $k$ best solutions, we need to make sure that we return $k$ different backtracks. To do that, we maintain a multiplicity counter in each backtrack process: \ul
\item While there is a single solution for all possible incoming paths, we continue in this direction with the same multiplicity (we have no choice).
\item When there is $r$ different solutions available, and the path multiplicity at this point is $k$ we have the following cases: \ol
	\item If $k\ge r$: we explore all paths with multiplicity $k-r+1$. This is because each branch may produce only one solution and we don't know ahead of time which path will provide multiple solutions. Finally, we retain only the $k$ best solutions.
	\item If $k<r$ (there is more paths than needed): we can only explore the $k$ first paths with multiplicity 1 and safely ignore the other (as we only need $k$ results).
	\ole
\ule

@@

Let one parser reversal complexity be $O(p)$, single backtrack has $O(2n\cdot p)$ complexity. For the $k$-elements backtrack, since we regenerate all possible solutions, that is $O(k^{c+1})$ candidates (with $c$ the maximal number of concatenation in the parser), the overall complexity is $O(2n \cdot k^{c+1} \cdot p)$. Hence there is a $k^{c+1}$ factor to pay if we want to backtrack the $k$ best solutions\footnote{Note that the same factor lies in the matrix computation complexity.}.

%Algo: Read matrix, reapply the parser but by maintaining list of origins. Filter results to match multiplicities
